Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-09-26 doc/part-hydras.tex
add a small remark
minor change in text

\subsubsection{A numerical example}

@@

>>>>

\subsubsection{A numerical example}
\label{sect:bignum}

@@

Since $H'_{\omega^3}(3)= H'_{\omega^3+3}(0)$, the big number shown in Section~\vref{sect:bignum} is less or equal than 
the number of steps of the battle with the initial hydra of
Figure~\ref{fig:start}, and  $0$ as initial replication factor.

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[very thick, scale=0.3]
  \node (h1) at (4,0){$\bullet$};
  \node (h2) at (2,2){$\bullet$};
  \node (h3) at (0,4){$\bullet$};
  \node (h4) at (1,4){$\bullet$};
  \node (h5) at (2,4){$\bullet$};
  \node (h6) at (4.5,2){$\bullet$};
  \node (h7) at (6.5,2){$\bullet$};
  \node (h8) at (8.5,2){$\bullet$};
    \draw (h1) -- (h2) ;
    \draw (h2) -- (h3) ;
    \draw (h2) -- (h4) ;
    \draw (h2) -- (h5) ;
    \draw (h1) -- (h6) ;
    \draw (h1) -- (h7) ;
    \draw (h1) -- (h8);
 \end{tikzpicture}

  \caption{The hydra corresponding to the ordinal $\omega^3+3$}
  \label{fig:start}
\end{figure}
